% !TEX root = 000_paper.tex

\section{The GATE Experiment}
\label{sec:GATE}

\ac{GATE} was a longitudinal study conducted by the US Department of Labor and the Small Business Administration in which free entrepreneurship training was randomly offered to individuals interested in starting or running a business. More than 4,000 individuals applied for a limited number of slots, making this, as of 2015, the largest-ever randomized evaluation of entrepreneurship training and assistance.

Subjects assigned to the treatment group were offered an array of (highly heterogeneous) free best-practice training services, while subjects assigned to the control group were not offered any free service. The treatment phase ran from September 2003 to July 2005 in five different sites across three states and, after the application survey, there were follow-up surveys at six, 18, and 60 months after random assignment.

The applicants' answers to the application survey provide a rich set of baseline characteristics. These include general information about age, gender, racial background and education; as well as information about household composition and socio-economics status, health, credit history, and employment. Personal characteristics associated with entrepreneurial success, which can be boiled down to two main (standardized) indexes of risk-tolerance and autonomy, were also assessed via these self-reported surveys.

Later follow-up surveys asked whether the individuals received GATE services since random assignment and how they evaluated the usefulness of those services; and contained questions on measures of business outcomes such as business ownership, business size and revenues, household income, and overall work satisfaction.

Fairlie, Kalran, and Zinman (2015) estimate the effects of receiving entrepreneurship training via GATE services (LATE). First, they check whether participating into the GATE experiment actually increased the quantity and quality of training received by the treated. Second, they estimate the impact of such training on a number of business outcomes at each time horizon, restricting the anaylsis to the complete case.

Their results suggest that entrepreneurship training had limited impacts on business ownership, scale, and household income. While entrepreneurship training did increase the likelihood of business ownership in the short-run (six months), this effect depreciated over time and was not significant anymore at 18 and 60 months. There is no evidence that training affected other outcomes at any horizon.

In this paper, we focus on the effects of being offered free entrepreneurship training (\ac{ITT}) on log household income 18 months after random assignment.

The main reason not to focus on a different measure, such as \ac{LATE}, is that defining what consists of ``proper'' treatment in the context of \ac{GATE} is not very straightforward. The services offered during the experiment were by design heterogeneous and personalized ---ranging from one-on-one counselling sessions to peer support to group training---, they were offered by a number of different organizations, and their content was not randomized. Moreover, we do not have information on receipt of training for all the individuals, which would mean further assumptions and/or variables to impute.

In principle, if entrepreneurship training is an investment in human capital (or functions as a signaling device on the labor market), recipients should have better financial outcomes than non-recipients, at least in the medium run; either because they are more likely to successfully start or run a business or because they are able to find or transition to better jobs. On the other hand, if recipients decide to invest their own savings in starting a business, this will have a negative impact on their household income. In general, the impact of being taught entrepreneurial skills is unclear, at least in developing countries (\cite{mckenzie2014}).
